Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
improved

\subsection{Basic Properties}
This section present some fundamental results of the clustering algorithm.
These are important, but do not change the larger picture. Thus we will not
spend too much time describing them. In short: more training samples is
better, more codes is better, larger patterns are more difficult.
\begin{itemize}
\item First, a larger dataset gives a better encoding codebook. See Figure
\ref{fig:data_sizes}.
\item Secondly, a larger codebook better encodes new song. See 
Table \ref{tab:cbsize}.
\item Finally, larger patterns are more difficult to encode, thus require
larger codebooks. See Figure \ref{fig:perbeat}.
\end{itemize}

These properties are important to verify and measure, but they are not
surprising for a clustering algorithm. We move on to more interesting facts.

>>>>

\subsection{Basic Properties}
This section present some fundamental results of the clustering algorithm.
These are important, but do not change the larger picture. Due to space
constraints, we give few details and refer to the figures.
\begin{itemize}
\item A larger dataset gives a better encoding codebook. See Figure
\ref{fig:data_sizes}.
\item A larger codebook better encodes new songs. See 
Table \ref{tab:cbsize}.
\item Larger patterns are more difficult to encode, thus require
larger codebooks. See Figure \ref{fig:perbeat}.
\end{itemize}

These properties are important to verify and for reproducing the experiments, 
but they are not surprising for a clustering algorithm.
